An effective sensor grid approach for large scale acoustic monitoring

### 2017-06-19 paper/article.tex
Paper update

\begin{abstract}
%% Text of abstract

@@

The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.

To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages. The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.

In our application setting, the requirements are the following. First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable. Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous. Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen. Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage

The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...). The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}. This detection step can respectively be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}. Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels. Furthermore, the detection is done once and cannot be recomputed during posterior analyses.

However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features. It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision. As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data. Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community. The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection. the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figures/censeCoder}
\vspace{-0.15in}
\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment. In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation. Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
\label{fig:codingScheme}
\end{figure}

\section{Background} \label{sec:background}

@@

\section{Encoding scheme} \label{sec:coder}

@@

\section{Validation protocol} \label{sec:protocol}

A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40. We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.

@@

\section{Results} \label{sec:results}

@@

The same set of parameters as in bitrate evaluation is used to study the impact of their tuing to the sound event recognition performance. We thus aim at finding ways to further reduce the encoded data size without strongly affecting recognition performance. Results of the four presented classification methods are provided for the sake of completeness.\\

@@

The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}. Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively. However, we find that given our setup, diminishing the number of analysis bands to some extent most often does notinduces a strong drop of performance. The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40. Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation. Time decimation is also possible, as in most cases the original data can be averaged \ml{consistently ?} and yield a good classification accuracy. The loss of information can be considered negligible for FPS values as low as 8 or 10 depending on the method. This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition performance. It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\fg{Highlight best/ok values once per class. method, not per fps}\\

\begin{table*}[h]
\centering
\caption{Classification accuracy for varying representation resolutions}
\label{T1}
\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & \textbf{0.60$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{0.61$\pm$0.04} & \textbf{0.63$\pm$0.03} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.62$\pm$0.03}} & \textbf{\textcolor{red}{0.63$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.67$\pm$0.05}} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & \textbf{0.42$\pm$0.03} & \textbf{\textcolor{red}{0.46$\pm$0.04}} & \textbf{\textcolor{red}{0.46$\pm$0.02}} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.03}} & \textbf{\textcolor{red}{0.46$\pm$0.05}} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{\textcolor{red}{0.43$\pm$0.05}} & \textbf{0.43$\pm$0.03} & 0.43$\pm$0.02 & \textbf{0.44$\pm$0.03} & \textbf{0.45$\pm$0.03} & \textbf{0.45$\pm$0.05} & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{0.42$\pm$0.04} & \textbf{0.43$\pm$0.02} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.05}} & \textbf{0.43$\pm$0.03} & \textbf{0.43$\pm$0.04} & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{0.42$\pm$0.06} & 0.43$\pm$0.03 & 0.43$\pm$0.03 & \textbf{0.42$\pm$0.03} & \textbf{0.44$\pm$0.03} & \textbf{0.46$\pm$0.03} & 0.45$\pm$0.04 \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & \textbf{0.43$\pm$0.02} & \textbf{0.51$\pm$0.04} & \textbf{0.53$\pm$0.04} & \textbf{0.53$\pm$0.05} & \textbf{0.53$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & \textbf{0.44$\pm$0.03} & \textbf{0.52$\pm$0.04} & \textbf{0.53$\pm$0.03} & \textbf{0.54$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & \textbf{0.45$\pm$0.04} & \textbf{\textcolor{red}{0.54$\pm$0.05}} & \textbf{\textcolor{red}{0.55$\pm$0.05}} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & \textbf{\textcolor{red}{0.46$\pm$0.03}} & \textbf{0.53$\pm$0.05} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.57$\pm$0.04}} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
\end{tabular}
\end{table*}

@@

We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms. Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands. Figure~\ref{fig:tob_mel_q} displays \fg{fig to be added} similar results to 40 bands, 8 fps mel spectrograms.\\

To further analyze both representations advantages, the confusion matrix is a reliable tool. It aims at providing information regarding class-by-class accuracy and misclassification rates. We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration. Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{mel_conf.eps}
	\caption{Confusion matrix for the same setup with 40 mel bands.}
	\label{fig:mel_conf}
\end{figure}
\fg{Ici je pensais pouvoir trouver et expliquer les differences dues au contenu des descripteurs, mais apparemment les résultats sont proches. TODO: creuser un peu plus, et conclure}

@@

Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions. Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{comment tu as fait le test ?} for the same setup. We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material. However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{int_mel_avg.eps}
	\caption{The two objective indicators computed for intelligibility assessment. Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
	\label{fig:int_mel_avg}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
	\caption{Results of a very small perceptual intelligibility test.}
	\label{fig:percint_mel_avg}
\end{figure}

@@

%% else use the following coding to input the bibitems directly in the
%% TeX file.
\section{References}

\bibliographystyle{plain}
\bibliography{biblio}

\ml{USE BIBTEX !!}

\begin{thebibliography}{09}

>>>>

\begin{abstract}
%% Text of abstract
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.

Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes. This detection step can be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted. Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.

But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

The coding scheme described in this paper has the following features. It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision. As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data. Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.

@@

As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.

The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.

requirements

scalability:
power managment:
security and privacy:
data richness:

low consumption computation (processing and transmission) of the sensor node

low bitrate of the transmitted data for efficient transmission and storage

proposed approach

%\begin{figure}[t]
%\includegraphics[width=\columnwidth]{figures/censeCoder}
%\vspace{-0.15in}
%\caption{}
%\label{fig:codingScheme}
%\end{figure}

\section{Background}

@@

\section{Encoding scheme}

@@

\section{Evaluation}
A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40. We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.

@@

\section{Results}

@@

The same set of parameters as in bitrate evaluation is used to study the impact of their tuning to the sound event recognition performance. We thus aim at finding ways to further reduce the encoded data size without strongly affecting recognition performance. Results of the four presented classification methods are provided for the sake of completeness.\\

@@

The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}. Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively. However, we find that given our setup, diminishing the number of analysis bands to some extent most often does not induce a strong drop of performance. The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40. Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation. Time decimation is also possible, as the original representation can be averaged and consistently yield a good classification accuracy. The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method. Even below, classification accuracy only drops by one or a few percents. This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition performance. It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\

\begin{table*}[h]
\centering
\caption{Classification accuracy for varying representation resolutions}
\label{T1}
\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & 0.61$\pm$0.04 & 0.62$\pm$0.03 & 0.62$\pm$0.04 & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & 0.58$\pm$0.04 & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & 0.60$\pm$0.03 & 0.64$\pm$0.04 & 0.64$\pm$0.04 & \textbf{0.65$\pm$0.04} & \textbf{0.65$\pm$0.03} & \textbf{0.67$\pm$0.04} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & 0.60$\pm$0.03 & 0.63$\pm$0.04 & \textbf{0.64$\pm$0.04} & 0.64$\pm$0.04 & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.60$\pm$0.03 & 0.62$\pm$0.03 & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.63$\pm$0.03 & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & 0.61$\pm$0.04 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.67$\pm$0.05} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} & 0.42$\pm$0.03 & \textbf{0.46$\pm$0.04} & 0.46$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & \textbf{0.46$\pm$0.05} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & 0.43$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & 0.45$\pm$0.05 & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & 0.42$\pm$0.04 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.04 & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & 0.42$\pm$0.06 & 0.43$\pm$0.03 & 0.43$\pm$0.03 & 0.42$\pm$0.03 & 0.44$\pm$0.03 & 0.46$\pm$0.03 & \textbf{0.46$\pm$0.04} \\ \cline{1-9}
\end{tabular}

\begin{tabular}{ll|c|c|c|c|c|c|c|}
\cline{3-9}
\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
 & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
 & \multicolumn{1}{|c|}{10} &0.43$\pm$0.02 & 0.51$\pm$0.04 & 0.53$\pm$0.04 & 0.53$\pm$0.05 & 0.53$\pm$0.04 & 0.54$\pm$0.04 & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{20} & 0.44$\pm$0.03 & 0.52$\pm$0.04 & 0.53$\pm$0.03 & 0.54$\pm$0.04 & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{30} & 0.45$\pm$0.04 & 0.54$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
\multicolumn{1}{|c}{}
 & \multicolumn{1}{|c|}{40} & 0.46$\pm$0.03 & 0.53$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.05} & \textbf{0.57$\pm$0.04} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
\end{tabular}
\end{table*}

@@

We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms. Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands. Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T1} for all classification schemes.\\

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{class_tob_q.eps}
	\caption{Classification accuracy with third-octave bands and varying word size.}
	\label{fig:class_tob_q}
\end{figure}

To further analyze both representations advantages, the confusion matrix is a reliable tool. It aims at providing information regarding class-by-class accuracy and misclassification rates. We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration. Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}. The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average. A noticeable difference is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases while third-octave are evenly distributed. The effect of this can be seen between classes 5 and 8 (resp. \textit{Drilling} and \textit{Jackhammer}). These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better. Conversely this improves globally class 1 (\textit{Air conditioning}) recognition as most of its defining components are situated in higher frequencies.\\

Each descriptor is thus found to have similar representational capabilities despite minor construction differences.

@@

\begin{figure}[h!]
	\centering
		\includegraphics[width=\columnwidth]{mel_conf.eps}
	\caption{Confusion matrix for the same setup with 40 mel bands.}
	\label{fig:mel_conf}
\end{figure}

@@

Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}. Figures~\ref{fig:csii_mel_avg} and \ref{fig:fwsnrseg_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions. Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup. For this test, subjects were asked to blindly listen to recovered speech audio with different representation and coding parameters. They had to rate each extract between 0 ans 5, respectively inintelligible and perfectly comprehensible. We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material. However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.

@@

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{csii_mel_avg.eps}
	\caption{The Coherence SII objective indicator computed for intelligibility assessment. Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
	\label{fig:csii_mel_avg}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{fwsnrseg_mel_avg.eps}
	\caption{Frequency-weighted segmental SNR for the same parameters.}
	\label{fig:fwsnrseg_mel_avg}
\end{figure}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
	\caption{Results of the perceptual intelligibility test.}
	\label{fig:percint_mel_avg}
\end{figure}

@@

%% else use the following coding to input the bibitems directly in the
%% TeX file.
\section{References}
\begin{thebibliography}{09}
